---
title: "Analysis"
author: "Arielle Smith with Claude assistance"
date: "2026-07-20"
output: html_document
---

```{r setup}
knitr::opts_knit$set(root.dir = "/Volumes/fsmresfiles/MSS/Schleider_Lab/jslab/ED SSI Delphi Study")
setwd("/Volumes/fsmresfiles/MSS/Schleider_Lab/jslab/ED SSI Delphi Study")
```

Phase 2 Round 1 analysis rules
- Rule 1 = Advance to Round 3: All four panels individually >= 80% Endorsed (aka rated as Very Important or Essential)
- Rule 2 = Reassess/re-rate in Round 2: NOT already Endorsed, AND all four panels individually >= 70% Endorsed aka Rule 2a OR any one panel >= 80% Endorsed aka Rule 2b
- Rule 3 = Dropped: Neither above condition met

Expert group labels:
1=A researcher focused on eating disorders; 
2=A clinician who treats people with eating disorders; 
3=A carer or supporter of someone with an eating disorder;
4=A person with lived experience of an eating disorder

Bridge item importance labels: 
1=Not sure/don’t know
2=Not important
3=Slightly important
4=Moderately important
5=Very important
6=Essential

```{r phase 2 round 1 calculations}
#Part 1: Calculate % endorsement ("very important" = 5 or "essential" = 6) for each item, within each of the 4 expert groups individually 
bridgeidea_pct_endorsed <- phase2_round1 %>%
  group_by(aim2r1_expert_group) %>% 
  summarise(across(
    c(contains("aim2r1_prvntion_"),  
      contains("aim2r1_ident_"),
      contains("aim2r1_ir_"),
      contains("aim2r1_treatmnt_"),
      contains("aim2r1_psorsrpt_")),
    # for each item column, calculate % of responses that were "5" or "6"
    # na.rm = TRUE excludes true missing/blank cells from the denominator;
    # an explicit "1" (not sure/don't know) is counted as non-endorsed
    ~ mean(.x %in% c("5", "6"), na.rm = TRUE) * 100
  ))

#Part 2: For each bridge idea, find the min/max % across the 4 expert groups (to be used in Part 3) and make a logical variable indicating if every expert group individually rated a bridge idea >= 70% 
bridgeidea_decision_wide <- bridgeidea_pct_endorsed %>%
  select(-aim2r1_expert_group) %>%
  summarise(across(
    everything(),
    list(
      min_pct  = ~min(.x, na.rm = TRUE),        # lowest group % Endorsed  (for Rule 1)
      max_pct  = ~max(.x, na.rm = TRUE),         # highest group % Endorsed (for Rule 2b)
      all_70   = ~all(.x >= 70, na.rm = TRUE)    # TRUE if every group is >= 70% Endorsed (for Rule 2a)
    ),
    .names = "{.col}__{.fn}" #syntax to create new column names (purposefully uses double underscore for later use as a separator)
  ))

bridgeidea_decision_tidy <- bridgeidea_decision_wide %>%
  pivot_longer(everything(), names_to = c("item_id", ".value"), names_sep = "__") %>%
  mutate(
    round1_decision = case_when(
      min_pct >= 80          ~ "Endorsed_R3",   # Rule 1 met, advance to Round 3
      all_70 | max_pct >= 80 ~ "Reassess_R2",    # Rule 2a met OR
                                                  # Rule 2b met, reassess in Round 2
      TRUE                   ~ "Dropped"         # Rule 3 met, drop bridge idea
    )
  )

#Part 4 (exploratory): Identify which expert group(s) met Rule 2b for given bridge idea

# reshape bridgeidea_pct_endorsed to long format: one row per item x expert group
bridgeidea_pct_long <- bridgeidea_pct_endorsed %>%
  pivot_longer(-aim2r1_expert_group, names_to = "item_id", values_to = "pct")

# for each item, list which group(s) hit >= 80%
groups_rule2b <- bridgeidea_pct_long %>%
  filter(pct >= 80) %>%
  group_by(item_id) %>%
  summarise(groups_meeting_rule2b = paste(aim2r1_expert_group, collapse = ", "))

# join into the existing decision table, then blank out rows that aren't Reassess_R2 (because Rule 2b is only relevant for this decision)
bridgeidea_decision_tidy <- bridgeidea_decision_tidy %>%
  left_join(groups_rule2b, by = "item_id") %>%
  mutate(groups_meeting_rule2b = if_else(round1_decision == "Reassess_R2",
                                          groups_meeting_rule2b,
                                          NA_character_))
```

I am concerned that keeping the pre-registered rule I have for Round 2 (moving on to Round 3 if 80% of all four panels individually rated as Very Important or Essential) will not lead to enough differentiation (too many items will fall in the grey area of 70-79% Endorsed). 

```{r exploratoration for round 2 analysis decision making}
 round2_test_min_pct <- bridgeidea_decision_tidy %>%
     filter(round1_decision == "Reassess_R2") %>%  # look at the pool that will be rerated in Round 2
    arrange(desc(min_pct)) %>%
    select(item_id, min_pct) # look at the lowest group % Endorsed (since this has to be above whatever threshold I set)
#Conclusion: 70% or 75% seems like a good cutoff point if Round 2 data mirrors Round 1 data for the bridge ideas that will be re-rated. It is also possible though that the original 80% threshold ends up being ok because after participants have seen group feedback, some additional convergence is expected. 
```